Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2021-11-07 proposalPres.tex
Update proposalPres.tex file
I tried to add gantt charts to the timeline and milestones slide, but was unable to do so.
Updated proposalPres.tex
Added Design slide, Simulation Results

@@

\begin{frame}{Simulation Results}
  \begin{block}{}
 \begin{itemize}
        \item 
	\item 
	\item 
\end{itemize}
  \end{block}
\end{frame}

>>>>

%----------------------------------
\section{Design}

\begin{frame}{Design}
	\begin{block}
		Each subsystem that we are modeling are set up in a similar manner. In manual mode, the torque voltages that control each subsystem are sent by the electronic control unit (ECU). In order to control the vehicle autonomously, the vehicle subsystem switches to by-wire mode. In by-wire mode, the torque voltages from the ECU are discarded by open-circuiting the motors that control each subsystem. Instead, controllers built by AutonomouStuff send the torque voltages to the motor using relays.
	\end{block}
\end{frame}

@@

\begin{frame}{Simulation Results}
  \begin{block}{}
 \begin{itemize}
	\item The best fit percentage of the by-wire steering estimated model is 85.54
	\item The best fit percentage of the manual steering estimated model is 90.27
 \end{itemize}
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2in]{figs/img/byWireSteeringTransferFunctionModel}
    \caption{Output of Estimated By-Wire System Model}
    \label{fig:byWireSteerModel}
\end{figure}
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2in]{figs/img/manualSteeringTransferFunctionModel}
    \caption{Output of Estimated Manual System Model}
    \label{fig:manualSteerModel}
\end{figure}
  \end{block}
\end{frame}
